\newpage

%\begin{comment}
\renewcommand{\bibname}{Библиографический список использованной литературы}
\begin{thebibliography}{99}
\vspace{5mm}
\addcontentsline{toc}{chapter}{Библиографический список использованной литературы}

\bibitem{baldoni:evolution}
Baldoni R. The evolution of publish/subscribe communication systems / 
R.~Baldoni, M.~Contenti, A.~Virgillito // Future Directions in Distributed Computing, ser. Lecture Notes in Computer Science. --- Springer, 2003. --- №2584. --- С. 137--141.

\bibitem{benson:talking}
Benson E. Talking about data: sharing richly structured information through blogs and wikis / 
E.~Benson, A.~Marcus, F.~Howahl, D.~Karger // Proc. 9th Int'l Conf. on The Semantic Web, ser. ISWC'10. Springer-Verlag. --- 2010. --- С. 48--63.

\bibitem{semantic}
Berners-Lee T. Scientific publishing on the semantic web / T. Berners-Lee, J. Hendler // Nature. --- 2001. --- №410. --- С. 1023--1024.

\bibitem{framling:smart}
Fr\"amling K. Smart Spaces for Ubiquitously Smart Buildings / K.~Fr\"amling, I. Oliver, J. Honkola, Jan Nyman // 
Proc. 3rd Int'l Conf. Mobile Ubiquitous Computing, Systems, Services and Technologies (UBICOMM 2009). --- 2009. --- С. 295--300.

\bibitem{guarino}
Guarino N. The Ontological Level: Revisiting 30 Years of Knowledge Representation / 
N.~Guarino // Conceptual modeling: Foundations and applications. --- Springer-Verlag, 2009. --- С. 52--67.

\bibitem{honkola:smart-m3}
Honkola J. Smart-M3 information sharing platform / J. Honkola, H.~Laine, R.~Brown, O. Tyrkk\"o
// The 1st Int’l Workshop on Semantic Interoperability for Smart Spaces
(SISS 2010) in conjunction with IEEE ISCC 2010. --- IEEE Computer Society,
2010. --- С. 295--300.

\bibitem{karger:what}
Karger D.~R. What would it mean to blog on the semantic web? / D.~R.~Karger, D.~Quan // 
Web Semant. --- 2005. --- №3. --- С. 147--157.

\bibitem{scblogging}
Korzun D.  Blogging in the Smart Conference System / D. Korzun, I.~Galov, A. Kashevnik, N. Shilov, K. Krinkin, Y. Korolev // Proc.~9th Conf. of Open Innovations Framework Program FRUCT. --- 2011. --- С.~63--73.

\bibitem{korzun:smartslog}
Korzun D. Generating Modest High-Level Ontology Libraries for Smart-M3 / D.~Korzun, A. Lomov, P. Vanag, 
J. Honkola, S. Balandin // Proc.~4th Int'l Conf. Mobile Ubiquitous Computing, Systems, Services and Technologies (UBICOMM 2010). --- 2010. --- С. 103--109.

\bibitem{oliver:context}
Oliver I. Context gathering in meetings: Business processes meet the Agents and the Semantic Web / 
I. Oliver, E. Nuutila, S. T{\"o}rm{\"a} // The 4th Int'l Workshop on Technologies for Context-Aware Business Process Management (TCoB 2009) within Proc. Joint Workshop on Advanced Technologies and Techniques for Enterprise Information Systems. --- 2009.

\bibitem{oliver:dynamic}
Oliver I. Dynamic, localised space based semantic webs / 
I. Oliver, J.~Honkola, J.~Ziegler //
Proc. IADIS Int’l Conf. WWW/Internet 2008. --- IADIS Press, 2008. --- С. 426--431.

\bibitem{rdf}
Resource Description Framework (RDF):
Concepts and Abstract Syntax [Электронный ресурс].
Режим доступа:
http://www.w3.org/TR/2004/REC-rdf-concepts-20040210/

\bibitem{m3weather}
Samoryadova A. M3-Weather: A Smart-M3 World-Weather Application for Mobile Users / A.~Samoryadova, I. Galov, P. Borovinskiy, K. Kulakov, D. Korzun // Proc. 8th Conf. of Open Innovations Framework Program FRUCT. --- 2010. --- С. 25--35.

\bibitem{foaf}
The friend of a friend (foaf) project [Электронный ресурс]. Режим доступа: http://www.foaf-project.org/

\bibitem{smartscribo}
Zaiceva D. A Blogging Application for Smart Spaces / D.~Zaiceva,
I.~Galov, A. Sannikov, D. Korzun // Proc. 9th Conf. of Open Innovations Framework Program FRUCT. --- 2011. --- С. 154--163.

\bibitem{smartscribo-old}
Zaiceva D. Mobile multi-blogging in Smart-M3: Architecture and scenarios / 
D. Zaiceva, I. Galov, A. Sannikov, D. Korzun // Proc. 8th Conf. of Open Innovations Framework Program FRUCT. --- 2010. --- С. 225--233.


\bibitem{scs}
Кашевник А. М. Интеллектуальная система автоматизированного проведения конференций / 
А. М. Кашевник, Ю. Вальченко, М. М. Ситаев, Н. Г. Шилов // Тр. СПИИРАН. --- 2010. --- №14. --- С. 228--243.

\end{thebibliography}

%\end{comment}

\bibliographystyle{gost71s}
\bibliography{references.bib}

%%%                          %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%